Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-11 Revise-version.tex
txs auto checkin

\subsection{Mathematical Modeling of Imperfections}
[Move here: Your AWGN equations:
\begin{equation}
\tilde{S}=S+\textbf{n}
\end{equation}
\begin{equation}
\tilde{n}=g_{L}(...g_{1}(\tilde{S}))
\end{equation}]

@@

\subsubsection{Noise Resilience}:
The model includes a mechanism to add Gaussian noise to the compressed CSI, simulating real-world noisy conditions. This addition helps in making the model robust against channel imperfections.

\subsubsection{Denoising Capability}:
The model incorporates a denoising network to remove the added noise. This network uses convolutional layers to clean the CSI feedback before it is further processed, ensuring high accuracy even under noisy conditions. In a symmetric manner, the convolution filters are also present in the decoder part of the architecture. Before the refinement step, we reshape the CSI matrix to 2×32×32 (Figure \ref{fig:figure3}).

@@

\begin{figure*}[!t]
	\centering
	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NMSEvsNofparametters.pdf}
		\caption{NMSE vs Number of Parameters}
		\label{fig:nmse-params}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.4\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NMSEvsFLOPs.pdf}
		\caption{NMSE vs FLOPs}
		\label{fig:nmse-flops}
	\end{minipage}
\end{figure*}

@@

\section{Proposed Denoising Framework}
\subsection{Architecture Design}
[Move here: Your federated learning approach description]
[Keep all details about noise power ranges (-5dB to 40dB)]

>>>>

\subsection{Mathematical Modeling of Feedback Imperfections}
\label{subsec:feedback_noise}

This analysis focuses exclusively on imperfections introduced \textit{during} the feedback transmission, assuming perfect channel estimation and compression at the UE. The two-stage noise model is:

\subsubsection{Noiseless Compression}
At the UE, the CSI matrix $\mathbf{H}_f$ is perfectly compressed to a codeword:

\begin{equation}
    \mathbf{s} = f_{\text{enc}}(\mathbf{H}_f)
\end{equation}

where $f_{\text{enc}}$ represents the ideal compression function.

\subsubsection{Feedback Channel Corruption}
During uplink transmission, the codeword is corrupted by AWGN:

\begin{equation}
    \tilde{\mathbf{s}} = \mathbf{s} + \mathbf{n}, \quad \mathbf{n} \sim \mathcal{CN}(0,\sigma_n^2\mathbf{I})
    \label{eq:noisy_feedback}
\end{equation}

with noise power $\sigma_n^2$ calculated from the uplink SNR:

\begin{equation}
    \sigma_n^2 = \frac{\mathbb{E}[\|\mathbf{s}\|_2^2]}{N_s \cdot 10^{\text{SNR}_{\text{dB}}/10}}
\end{equation}

where $N_s$ is the codeword length.

\subsubsection{Denoising and Reconstruction}
The BS applies a denoising operator $\mathcal{D}$ to obtain:

\begin{equation}
    \hat{\mathbf{s}} = \mathcal{D}(\tilde{\mathbf{s}})
\end{equation}

followed by ideal reconstruction:

\begin{equation}
    \hat{\mathbf{H}}_f = f_{\text{dec}}(\hat{\mathbf{s}})
\end{equation}

\subsubsection{Error Decomposition}
The total NMSE contains only feedback-induced errors:

\begin{equation}
    \text{NMSE} = \underbrace{\frac{\mathbb{E}[\|\mathbf{H}_f - f_{\text{dec}}(\mathbf{s})\|_F^2]}{\|\mathbf{H}_f\|_F^2}}_{\text{Compression error}} + \underbrace{\frac{\mathbb{E}[\|f_{\text{dec}}(\mathbf{s}) - f_{\text{dec}}(\hat{\mathbf{s}})\|_F^2]}{\|\mathbf{H}_f\|_F^2}}_{\text{Denoising error}}
\end{equation}

\begin{itemize}
    \item \textbf{Key Assumption}: Channel estimation errors and pre-compression noise are negligible ($\mathbf{H}_f$ is perfect)
    \item \textbf{Scope}: All noise enters through the feedback channel (\eqref{eq:noisy_feedback})
\end{itemize}

@@

\subsubsection{Noise Resilience} 
\label{subsubsec:noise_resilience}

The system maintains robust performance across noise conditions through:

\begin{itemize}
    \item \textbf{SNR-Adaptive Processing}:
    \begin{equation}
        \alpha(\gamma) = 1 - e^{-\gamma/10}
    \end{equation}

    \item \textbf{Structured Latent Space}:
    \begin{equation}
        \|\mathbf{s} - \mathbf{s}'\|_2 \leq \epsilon \Rightarrow \|f_{\text{dec}}(\mathbf{s}) - f_{\text{dec}}(\mathbf{s}')\|_F \leq C\epsilon
    \end{equation}

    \item \textbf{Quantization Robustness}:
    \begin{equation}
        \mathbb{E}[\|\mathbf{s}_q - \mathbf{s}\|_2^2] \leq \frac{\Delta^2 N_s}{12}
    \end{equation}
\end{itemize}

\subsubsection{Denoising Capability} 
\label{subsubsec:denoising}

The denoising module provides:

\begin{itemize}
    \item \textbf{Multi-Path Processing}:
    \begin{equation}
        \hat{\mathbf{n}} = \sum_{k} w_k \cdot \text{Conv1x}k(\tilde{\mathbf{s}})
    \end{equation}

    \item \textbf{Residual Learning}:
    \begin{equation}
        \mathcal{L}_{\text{denoise}} = \|\hat{\mathbf{n}} - \mathbf{n}\|_1 + \lambda\|\nabla\hat{\mathbf{n}}\|_2^2
    \end{equation}
\end{itemize}

@@

\begin{figure*}[!t]

	\begin{minipage}[b]{0.4\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NMSEvsFLOPs.pdf}
		\caption{NMSE vs FLOPs}
		\label{fig:nmse-flops}
	\end{minipage}
\end{figure*}

@@
